### 2018-12-04 Sections/quantum_algorithms.tex
Economics update. Roadmap update.
indexing

The algorithm relies on a `black box', referred to as an \textit{oracle}\index{Oracles}, which takes an input bit-string and outputs a single bit, evaluating the function $f(x)$ for the $n$-bit input bit-string $x$. In this contrived problem $f(x)$ is guaranteed to be either \textit{uniform}\index{Uniform functions} or \textit{balanced}\index{Balanced functions}. In the former case, the output to the oracle is always \mbox{$f(x)=0$} or always \mbox{$f(x)=1$}, but it doesn't matter which, they simply must always be the same. In the latter case, the output is \mbox{$f(x)=0$} for exactly half the inputs $x$, and \mbox{$f(x)=1$} for the other half of $x$, but the ordering of which inputs generate which outputs may be arbitrary. The goal of the algorithm is to determine whether $f(x)$ is uniform of balanced using the least number of queries to the oracle.

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QFT($\ket{x}$):
\begin{enumerate}
\item Apply the recursively-defined circuit below to the $n$-qubit input state $\ket{x}$, where,
\begin{align}
\hat{R}_\theta=\left(\begin{matrix}
1 & 0 \\
0 & e^{i\theta}	
\end{matrix}\right),
\end{align}
is a generalised phase-flip gate.
\item The amplitudes in the $n$-qubit output state $\ket{y}$ are given by the quantum Fourier transform of the input amplitudes, implementing the transformation,
\begin{align}
	\hat{\mathrm{QFT}} \ket{j} \to \frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} \omega^{jk}\ket{k},
\end{align}
on the logical basis states, or in matrix form,
\begin{align}
\frac{1}{\sqrt{N}} \left(\begin{matrix}
  1 & 1 & 1 & \dots & 1\\
  1 & \omega & \omega^2 & \dots & \omega^{N-1} \\
  1 & \omega^2 & \omega^4 & \dots & \omega^{2(N-1)} \\
  \vdots & \vdots & \vdots & \ddots & \vdots \\
  1 & \omega^{N-1} & \omega^{2(N-1)} &\dots &\omega^{(N-1)(N-1)}
\end{matrix}\right),
\end{align}
where there are,
\begin{align}
N=2^n,
\end{align}
logical basis states.
\item The quantum circuit requires $O(n^2)$ gates.
\item Return $\ket{y}$.
\item $\Box$
\end{enumerate}
\begin{center}
\if 2\pubmode
\includegraphics[width=\textwidth]{QFT}
\else
\includegraphics[width=0.75\textwidth]{QFT}
\fi
\end{center}
}
\end{mdframed}
\captionspacealg \caption{The quantum Fourier transform (QFT) algorithm. The circuit is defined recursively, defining the $n$-qubit QFT in terms of an \mbox{$n-1$}-qubit QFT.} \label{alg:QFT}\index{Quantum Fourier transform}
\end{table}

@@

\subsection{Integer factorisation} \index{Shor's algorithm}\index{Hidden subgroup problem}\index{Period finding}
	\index{Integer factorisation}\label{sec:shors_alg}

@@

Shor's algorithm works by first reducing integer factorisation to another problem, \textit{period finding}\index{Period finding}. For the function,
\begin{align}
f(x)= a^x \,\mathrm{mod}\, N,	
\end{align}
find its period \mbox{$r\in\mathbb{Z}^+$}, the smallest integer such that,
\begin{align}
f(x)=f(x+r) \,\mathrm{mod}\, N.	
\end{align}
With the ability to solve the period finding problem, an efficient classical algorithm exists for transforming this solution to a solution for factoring.

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Shor(a,N):
\begin{enumerate}
	\item For function,
	\begin{align}
		f(x)= a^x \,\mathrm{mod}\, N,	
	\end{align}
	we wish to find the smallest integer $r$ such that,
	\begin{align}
		f(x)=f(x+r) \,\mathrm{mod} \,N.	
	\end{align}
	\item Run the circuit below.
	\item Efficient classical processing of the measured output registers reveals $r$ with high probabiliy.
	\item Classically verify that,
	\begin{align}
		f(x)=f(x+r) \,\mathrm{mod} \,N.	
	\end{align}
	\item If it isn't then repeat the circuit to obtain more samples. 
    \item $\Box$
\end{enumerate}
\begin{center}
\if 2\pubmode
\includegraphics[width=\textwidth]{shor_circuit}
\else
\includegraphics[width=0.55\textwidth]{shor_circuit}
\fi
\end{center}
}
\end{mdframed}
\captionspacealg \caption{Shor's quantum algorithm for integer factorisation.} \label{alg:shor}
\end{table}

@@

Although not as obviously algorithmically useful as decision problems, sampling problems have received much interest owing to their generally very simple construction. For example, \textsc{BosonSampling} requires only single-photon inputs, evolved via a passive linear optics\index{Linear optics} beamsplitter network, and measured using photo-detection\index{Photo-detection}. IQP sampling requires only single-qubit Hadamard gates\index{Hadamard!Gate} and generalised multi-qubit controlled-phase gates\index{Generalised controlled-phase gates}\footnote{Generalised CZ gates are simply gates diagonal in the logical basis, where the diagonal elements are arbitrary phases, \mbox{$\hat{U}_\mathrm{CZ} = \mathrm{diag}(e^{i\theta_1},\dots,e^{i\theta_n})$}.}, thereby sampling from the logical state,
\begin{align}
\ket{\psi_\mathrm{out}} = \hat{H}^{\otimes n} \cdot \hat{U}_\mathrm{CZs} \cdot \hat{H}^{\otimes n} \ket{0}^{\otimes n}.	
\end{align}
Because CZ gates commute, they can be performed in parallel, giving the IQP circuit construction very low circuit depth\index{Circuit depth}. The IQP protocol is shown in Alg.~\ref{alg:IQP_samp}.

>>>>

The algorithm relies on a `black box', referred to as an \textit{oracle}\index{Oracles}, which takes an input bit-string and outputs a single bit, evaluating the function $f(x)$ for the $n$-bit input bit-string $x$. In this contrived problem $f(x)$ is guaranteed to be either \textit{uniform}\index{Uniform functions} or \textit{balanced}\index{Balanced!Functions}. In the former case, the output to the oracle is always \mbox{$f(x)=0$} or always \mbox{$f(x)=1$}, but it doesn't matter which, they simply must always be the same. In the latter case, the output is \mbox{$f(x)=0$} for exactly half the inputs $x$, and \mbox{$f(x)=1$} for the other half of $x$, but the ordering of which inputs generate which outputs may be arbitrary. The goal of the algorithm is to determine whether $f(x)$ is uniform of balanced using the least number of queries to the oracle.

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QFT($\ket{x}$):
\begin{enumerate}
\item Apply the recursively-defined circuit below to the $n$-qubit input state $\ket{x}$, where,
\begin{align}
\hat{R}_\theta=\left(\begin{matrix}
1 & 0 \\
0 & e^{i\theta}	
\end{matrix}\right),
\end{align}
is a generalised phase-flip gate.
\item The amplitudes in the $n$-qubit output state $\ket{y}$ are given by the quantum Fourier transform of the input amplitudes, implementing the transformation,
\begin{align}
	\hat{\mathrm{QFT}} \ket{j} \to \frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} \omega^{jk}\ket{k},
\end{align}
on the logical basis states, or in matrix form,
\begin{align}
\frac{1}{\sqrt{N}} \left(\begin{matrix}
  1 & 1 & 1 & \dots & 1\\
  1 & \omega & \omega^2 & \dots & \omega^{N-1} \\
  1 & \omega^2 & \omega^4 & \dots & \omega^{2(N-1)} \\
  \vdots & \vdots & \vdots & \ddots & \vdots \\
  1 & \omega^{N-1} & \omega^{2(N-1)} &\dots &\omega^{(N-1)(N-1)}
\end{matrix}\right),
\end{align}
where there are,
\begin{align}
N=2^n,
\end{align}
logical basis states.
\item The quantum circuit requires $O(n^2)$ gates.
\item Return $\ket{y}$.
\item $\Box$
\end{enumerate}
\begin{center}
\if 2\pubmode
\includegraphics[clip=true, width=\textwidth]{QFT}
\else
\includegraphics[clip=true, width=0.75\textwidth]{QFT}
\fi
\end{center}
}
\end{mdframed}
\captionspacealg \caption{The quantum Fourier transform (QFT) algorithm. The circuit is defined recursively, defining the $n$-qubit QFT in terms of an \mbox{$n-1$}-qubit QFT.} \label{alg:QFT}\index{Quantum Fourier transform}
\end{table}

@@

\subsection{Integer factorisation} \index{Shor's algorithm}\index{Hidden subgroup problem}\index{Period-finding}
	\index{Integer factorisation}\label{sec:shors_alg}

@@

Shor's algorithm works by first reducing integer factorisation to another problem, \textit{period finding}\index{Period-finding}. For the function,
\begin{align}
f(x)= a^x \,\mathrm{mod}\, N,	
\end{align}
find its period \mbox{$r\in\mathbb{Z}^+$}, the smallest integer such that,
\begin{align}
f(x)=f(x+r) \,\mathrm{mod}\, N.	
\end{align}
With the ability to solve the period finding problem, an efficient classical algorithm exists for transforming this solution to a solution for factoring.

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Shor(a,N):
\begin{enumerate}
	\item For function,
	\begin{align}
		f(x)= a^x \,\mathrm{mod}\, N,	
	\end{align}
	we wish to find the smallest integer $r$ such that,
	\begin{align}
		f(x)=f(x+r) \,\mathrm{mod} \,N.	
	\end{align}
	\item Run the circuit below.
	\item Efficient classical processing of the measured output registers reveals $r$ with high probabiliy.
	\item Classically verify that,
	\begin{align}
		f(x)=f(x+r) \,\mathrm{mod} \,N.	
	\end{align}
	\item If it isn't then repeat the circuit to obtain more samples. 
    \item $\Box$
\end{enumerate}
\begin{center}
\if 2\pubmode
\includegraphics[clip=true, width=\textwidth]{shor_circuit}
\else
\includegraphics[clip=true, width=0.55\textwidth]{shor_circuit}
\fi
\end{center}
}
\end{mdframed}
\captionspacealg \caption{Shor's quantum algorithm for integer factorisation.} \label{alg:shor}
\end{table}

@@

Although not as obviously algorithmically useful as decision problems, sampling problems have received much interest owing to their generally very simple construction. For example, \textsc{BosonSampling} requires only single-photon inputs, evolved via a passive linear optics\index{Linear optics} beamsplitter network, and measured using photo-detection\index{Photo-detection}. IQP sampling requires only single-qubit Hadamard gates\index{Hadamard!Gate} and generalised multi-qubit controlled-phase gates\index{Generalised controlled-phase gates}\footnote{Generalised CZ gates are simply gates diagonal in the logical basis, where the diagonal elements are arbitrary phases, \mbox{$\hat{U}_\mathrm{CZ} = \mathrm{diag}(e^{i\theta_1},\dots,e^{i\theta_n})$}.}, thereby sampling from the logical state,
\begin{align}
\ket{\psi_\mathrm{out}} = \hat{H}^{\otimes n} \cdot \hat{U}_\mathrm{CZs} \cdot \hat{H}^{\otimes n} \ket{0}^{\otimes n}.	
\end{align}
Because CZ gates commute, they can be performed in parallel, giving the IQP circuit construction very low circuit depth\index{Circuit!Depth}. The IQP protocol is shown in Alg.~\ref{alg:IQP_samp}.

### 2018-12-04 Sections/quantum_genetic_medicine.tex
indexing

The first complete mapping of the human genome was a major scientific achievement \cite{humanGenomeProject}, opening up entirely new avenues for medical research\index{Medical research} that were previously never possible. It was, however, an extraordinarily expensive undertaking, costing on the order of \$1b.

@@

The other approach, \textit{mapping}, is to use an existing genome as a reference\index{Genome!Reference}. Rather than piece short-reads together, we compare them against this reference to infer their relative locations in the genome. When doing so, we allow some error threshold\index{Error threshold} in the matching. Specifically, we require the Hamming distance\index{Hamming distance} between a short-read and an equally-long segment of the reference be below some threshold. The flexibility offered by this threshold accommodates for mutational differences between the reference and the short-reads\index{Genetics!Mutations} (i.e the SNPs), which is ultimately what we wish to characterise.

@@

At its simplest, the design of genetically-tailored medical treatments will require understanding the interactions between drug compounds\index{Drug compounds} and genetic processes at the molecular level. For example, we might desire that a drug modifies gene expression\index{Gene expression} for specific genes, or the transcription\index{Transcription} of DNA\index{DNA} to specific proteins\index{Proteins}. In the case of cancer treatment, we may wish to inhibit the function of biochemical processes\index{Biochemical processes} reliant on genes exhibiting particular cancerous mutations\index{Genetics!Mutations}, whilst not affecting healthy, unmutated ones.

@@

The key goal is to properly simulate the interaction of candidate drug compounds\index{Drug compounds}, ligands\index{Ligands}, or functional groups\index{Functional groups} with biochemical processes at the molecular level. Classical techniques for such simulations include estimating electron densities using density functional theory\index{Electron density}\index{Density functional theory} (the potential energy surface)\index{Electron density} of compounds, from which useful properties such as bonding affinities\index{Bonding affinity} may be estimated.

@@

These Hamiltonians can be constructed \textit{ab initio}, combining relevant one- and two-body interactions\index{One-body interactions}\index{Two-body interactions}, such as Coulomb potential\index{Coulomb potential}, kinetic energy\index{Kinetic energy}, spin- and spin-orbit\index{Spin coupling}\index{Spin-orbit coupling} coupling, and magnetic and electric dipole terms appropriately. A net interaction Hamiltonian may be obtained by summing over the different one- ($i$) and two-body (\mbox{$j,k$}) terms for all particles comprising the system,
\begin{align}
	\hat{H}_\mathrm{int} = \sum_i \hat{H}_i + \sum_{j>k} \hat{H}_{j,k}.
\end{align}
This structure is of the form of Eq.~(\ref{eq:Ham_sim_Ham}) and thus lends itself to the quantum Hamiltonian simulation algorithm\index{Quantum simulation} (Sec.~\ref{sec:quantum_sim_alg}).

The dominant one-body interactions are kinetic energy\index{Kinetic energy!Hamiltonian} terms, of the form,
\begin{align}
\hat{H}_i^{(\mathrm{kinetic})} &= \frac{\hat{p}^2}{2m} \nonumber \\
&= -\frac{\hbar^2}{2m_i}\nabla^2_{\vec{r}_i},
\end{align}
where $\hat{p}$ is the momentum operator, $m_i$ is mass, $\vec{r}_i$ is the position vector, and,
\begin{align}
\nabla^2 = \frac{\partial^2}{\partial x^2} + \frac{\partial^2}{\partial y^2} + \frac{\partial^2}{\partial z^2}.
\end{align}
The dominant two-body terms are Coulomb (electrostatic) interactions\index{Coulomb interaction},
\begin{align}
\hat{H}_{j,k}^{(\mathrm{Coulomb})} = \frac{q_j q_k}{4\pi\epsilon_0|\vec{r}_j-\vec{r}_k|},
\end{align}
where $q_j$ denotes charge.

@@

These approaches borrowed from quantum chemistry allow simulation of the interaction between drug compounds and molecular biochemical interactions. The next step is to perform this process against a huge library of candidate drug compounds\index{Drug compounds!Libraries}, ligands or functional groups, from which, we hope, some candidates will exhibit desired characteristics, such as strong bonding affinities\index{Bonding affinity}.

@@

An R\&D organisation might specialise in the algorithmic generation\index{Algorithmic generation} (or hard-coding\index{Hard-coding}) of candidate drug compounds\index{Compounds}, which they would like to retain as a trade secret\index{Trade secrets}, but desire to license\index{Outsourced!Quantum computation} to third-party drug designers\index{Drug design}, who wish to employ them in their computational pipeline\index{Quantum drug trial simulations}. The quantum search\index{Grover's algorithm} and Hamiltonian simulation\index{Quantum simulation} subroutines might similarly be outsourced or distributed over the cloud to vendors specialising in the implementation of these particular subroutines.

In an era where the genetic composition of every individual is fully characterised, data security will be of utmost importance -- medical confidentiality\index{Medical confidentiality} will be lifted to an entirely new plane when people's genes are at stake, as the nefarious uses (and misuses\index{Nefarious uses}) for obtaining other people's genomes are immense. This provides a perfect example for the value of encrypted quantum computation\index{Encrypted quantum computation} (Sec.~\ref{sec:homo_blind}). If a medical lab is outsourcing some aspects of a computation involving clients' genetics, it is paramount that this be obscured from third-parties performing the computations in the interest of medical confidentiality. Computational efficiency aside, this consideration on its own already justifies implementing such simulation pipelines quantum mechanically, as encrypted classical computation is effectively unviable in general.

>>>>

The first complete mapping of the human genome was a major scientific achievement \cite{humanGenomeProject}, opening up entirely new avenues for medical research\index{Medical!Research} that were previously never possible. It was, however, an extraordinarily expensive undertaking, costing on the order of \$1b.

@@

The other approach, \textit{mapping}, is to use an existing genome as a reference\index{Genome!Reference}. Rather than piece short-reads together, we compare them against this reference to infer their relative locations in the genome. When doing so, we allow some error threshold\index{Error!Threshold} in the matching. Specifically, we require the Hamming distance\index{Hamming distance} between a short-read and an equally-long segment of the reference be below some threshold. The flexibility offered by this threshold accommodates for mutational differences between the reference and the short-reads\index{Genetics!Mutations} (i.e the SNPs), which is ultimately what we wish to characterise.

@@

At its simplest, the design of genetically-tailored medical treatments will require understanding the interactions between drug compounds\index{Drug!Compounds} and genetic processes at the molecular level. For example, we might desire that a drug modifies gene expression\index{Gene expression} for specific genes, or the transcription\index{Transcription} of DNA\index{DNA} to specific proteins\index{Proteins}. In the case of cancer treatment, we may wish to inhibit the function of biochemical processes\index{Biochemical processes} reliant on genes exhibiting particular cancerous mutations\index{Genetics!Mutations}, whilst not affecting healthy, unmutated ones.

@@

The key goal is to properly simulate the interaction of candidate drug compounds\index{Drug!Compounds}, ligands\index{Ligands}, or functional groups\index{Functional groups} with biochemical processes at the molecular level. Classical techniques for such simulations include estimating electron densities using density functional theory\index{Electron density}\index{Density functional theory} (the potential energy surface)\index{Electron density} of compounds, from which useful properties such as bonding affinities\index{Bonding affinity} may be estimated.

@@

These Hamiltonians can be constructed \textit{ab initio}, combining relevant one- and two-body interactions\index{One-body interactions}\index{Two-body interactions}, such as Coulomb potential\index{Coulomb!Potential}, kinetic energy\index{Kinetic energy}, spin- and spin-orbit\index{Spin coupling}\index{Spin-orbit coupling} coupling, and magnetic and electric dipole terms appropriately. A net interaction Hamiltonian may be obtained by summing over the different one- ($i$) and two-body (\mbox{$j,k$}) terms for all particles comprising the system,
\begin{align}
	\hat{H}_\mathrm{int} = \sum_i \hat{H}_i + \sum_{j>k} \hat{H}_{j,k}.
\end{align}
This structure is of the form of Eq.~(\ref{eq:Ham_sim_Ham}) and thus lends itself to the quantum Hamiltonian simulation algorithm\index{Quantum simulation} (Sec.~\ref{sec:quantum_sim_alg}).

The dominant one-body interactions are kinetic energy\index{Kinetic energy!Hamiltonian} terms, of the form,
\begin{align}
\hat{H}_i^{(\mathrm{kinetic})} &= \frac{\hat{p}^2}{2m} \nonumber \\
&= -\frac{\hbar^2}{2m_i}\nabla^2_{\vec{r}_i},
\end{align}
where $\hat{p}$ is the momentum operator, $m_i$ is mass, $\vec{r}_i$ is the position vector, and,
\begin{align}
\nabla^2 = \frac{\partial^2}{\partial x^2} + \frac{\partial^2}{\partial y^2} + \frac{\partial^2}{\partial z^2}.
\end{align}
The dominant two-body terms are Coulomb (electrostatic) interactions\index{Coulomb!Interaction},
\begin{align}
\hat{H}_{j,k}^{(\mathrm{Coulomb})} = \frac{q_j q_k}{4\pi\epsilon_0|\vec{r}_j-\vec{r}_k|},
\end{align}
where $q_j$ denotes charge.

@@

These approaches borrowed from quantum chemistry allow simulation of the interaction between drug compounds and molecular biochemical interactions. The next step is to perform this process against a huge library of candidate drug compounds\index{Drug!Compounds!Libraries}, ligands or functional groups, from which, we hope, some candidates will exhibit desired characteristics, such as strong bonding affinities\index{Bonding affinity}.

@@

An R\&D organisation might specialise in the algorithmic generation\index{Algorithmic generation} (or hard-coding\index{Hard-coding}) of candidate drug compounds\index{Compounds}, which they would like to retain as a trade secret\index{Trade secrets}, but desire to license\index{Outsourced!Quantum computation} to third-party drug designers\index{Drug!Design}, who wish to employ them in their computational pipeline\index{Quantum drug trial simulations}. The quantum search\index{Grover's algorithm} and Hamiltonian simulation\index{Quantum simulation} subroutines might similarly be outsourced or distributed over the cloud to vendors specialising in the implementation of these particular subroutines.

In an era where the genetic composition of every individual is fully characterised, data security will be of utmost importance -- medical confidentiality\index{Medical!Confidentiality} will be lifted to an entirely new plane when people's genes are at stake, as the nefarious uses (and misuses\index{Nefarious uses}) for obtaining other people's genomes are immense. This provides a perfect example for the value of encrypted quantum computation\index{Encrypted quantum computation} (Sec.~\ref{sec:homo_blind}). If a medical lab is outsourcing some aspects of a computation involving clients' genetics, it is paramount that this be obscured from third-parties performing the computations in the interest of medical confidentiality. Computational efficiency aside, this consideration on its own already justifies implementing such simulation pipelines quantum mechanically, as encrypted classical computation is effectively unviable in general.

### 2018-12-04 Sections/quantum_repeater_networks.tex
Formatting, algs
Figure resizing. minor.
indexing

 For example, a satellite in low Earth orbit (Sec.~\ref{sec:quant_space_race}) may be outside simultaneous line-of-sight\index{Line-of-sight} to two distinct ground stations\index{Ground stations}, owing simply to the curvature of the Earth\index{Earth curvature}. But this can be overcome by relaying a channel through several satellites in line-of-sight of one another. This is achieved using a bootstrapped entanglement swapping and purification protocol (Secs.~\ref{sec:swapping} \& \ref{sec:ent_purif}). Most commonly, this entanglement is in the form of Bell pairs\index{Bell states}, which, as discussed previously in Sec.~\ref{sec:ent_ultimate}, form a ubiquitous resource for many essential quantum protocols. The actual physical encoding of the entangled states may vary, but is most commonly and archetypically in the form of polarisation-encoded\index{Polarisation encoding} single-photons or CV states\index{Continuous-variables!States}.

@@

One immediately notices that the $\ket{g} \ket{e}$ and $\ket{e}\ket{g}$ contributions are associated with two photons in one of the PBS exit modes, the other being in the vacuum state. However, the $\ket{g}\ket{g}$ and $\ket{e}\ket{e}$ terms have one photon in each of the output modes. They are of opposite polarisation, but measuring those photons in the diagonal/anti-diagonal ($\hat{X}$) basis erases this `which-path' information\index{Which-path erasure} yielding an equal superposition of the two alternative histories -- an entangled Bell state\index{Bell states} of the form,
\begin{align}
\ket{\Psi_\pm}=\frac{1}{\sqrt{2}} (\ket{g}\ket{g} \pm \ket{e}\ket{e}),
\end{align}
where the sign is given by the parity of the two photo-detection outcomes in the $\hat{X}$ basis. This entangled state is stored in the quantum memories between nodes.

@@

\subsubsection{Loss-tolerant codes}\index{Loss-tolerance!Codes}

@@

As can seen the various quantum repeater generations take quite different approaches as to how they distribute entanglement between Alice and Bob over a long distance \cite{bib:Muralidharan2016}. It is useful thus to summarise in Table.~\ref{tab:rep_nets_scale} the performance of the various repeater approaches and their requirements.

@@

\begin{figure}[!htbp]
\if 3\pubmode
	\includegraphics[clip=true, width=0.8\textwidth]{racetime}
\else
	\includegraphics[clip=true, width=0.475\textwidth]{racetime}
\fi
\captionspacefig \caption{A linear quantum repeater network comprising Bell pair sources, and Bell measurements for entanglement swapping (there is no purification stage in this example). Upon success this yields a single Bell pair between the leftmost and rightmost photonic qubits. $t_i$ is the triggering time of the $i$th source, and $\tau_i^\leftarrow$ ($\tau_i^\rightarrow$) are the channel propagation times between the $i$th source and the entanglement swapper to its immediate left (right). With push-button sources\index{Push-button source}, if the $t_i$ are chosen appropriately, as per Eq.~(\ref{eq:repeater_trig_time_sol}), we can satisfy the race-time condition\index{Race-time conditions} of simultaneous arrival times of photons at Bell measurements, mitigating the need for quantum memories to synchronise them.}\label{fig:racetime}	
\end{figure}

>>>>

 For example, a satellite in low Earth orbit (Sec.~\ref{sec:quant_space_race}) may be outside simultaneous line-of-sight\index{Line-of-sight} to two distinct ground stations\index{Ground stations}, owing simply to the curvature of the Earth\index{Earth curvature}. But this can be overcome by relaying a channel through several satellites in line-of-sight of one another. This is achieved using a bootstrapped entanglement swapping and purification protocol (Secs.~\ref{sec:swapping} \& \ref{sec:ent_purif}). Most commonly, this entanglement is in the form of Bell pairs\index{Bell!States}, which, as discussed previously in Sec.~\ref{sec:ent_ultimate}, form a ubiquitous resource for many essential quantum protocols. The actual physical encoding of the entangled states may vary, but is most commonly and archetypically in the form of polarisation-encoded\index{Polarisation encoding} single-photons or CV states\index{Continuous-variables!States}.

@@

One immediately notices that the $\ket{g} \ket{e}$ and $\ket{e}\ket{g}$ contributions are associated with two photons in one of the PBS exit modes, the other being in the vacuum state. However, the $\ket{g}\ket{g}$ and $\ket{e}\ket{e}$ terms have one photon in each of the output modes. They are of opposite polarisation, but measuring those photons in the diagonal/anti-diagonal ($\hat{X}$) basis erases this `which-path' information\index{Which-path erasure} yielding an equal superposition of the two alternative histories -- an entangled Bell state\index{Bell!States} of the form,
\begin{align}
\ket{\Psi_\pm}=\frac{1}{\sqrt{2}} (\ket{g}\ket{g} \pm \ket{e}\ket{e}),
\end{align}
where the sign is given by the parity of the two photo-detection outcomes in the $\hat{X}$ basis. This entangled state is stored in the quantum memories between nodes.

@@

\subsubsection{Loss-tolerant codes}\index{Loss!Tolerance!Codes}

@@

As can seen the various quantum repeater generations take quite different approaches as to how they distribute entanglement between Alice and Bob over a long distance \cite{bib:Muralidharan2016}. It is useful thus to summarise in Tab.~\ref{tab:rep_nets_scale} the performance of the various repeater approaches and their requirements.

@@

\begin{figure*}[!htbp]
\if 3\pubmode
	\includegraphics[clip=true, width=0.8\textwidth]{racetime}
\else
	\includegraphics[clip=true, width=0.8\textwidth]{racetime}
\fi
\captionspacefig \caption{A linear quantum repeater network comprising Bell pair sources, and Bell measurements for entanglement swapping (there is no purification stage in this example). Upon success this yields a single Bell pair between the leftmost and rightmost photonic qubits. $t_i$ is the triggering time of the $i$th source, and $\tau_i^\leftarrow$ ($\tau_i^\rightarrow$) are the channel propagation times between the $i$th source and the entanglement swapper to its immediate left (right). With push-button sources\index{Push-button source}, if the $t_i$ are chosen appropriately, as per Eq.~(\ref{eq:repeater_trig_time_sol}), we can satisfy the race-time condition\index{Race-time conditions} of simultaneous arrival times of photons at Bell measurements, mitigating the need for quantum memories to synchronise them.}\label{fig:racetime}	
\end{figure*}

### 2018-12-04 Sections/state_of_the_art.tex
indexing

\subsection{Entangled states based on non-linear optics} \index{Non-linear optics}

@@

\subsection{Atomic ensembles} \index{Atomic ensembles}

A variety of techniques have been developed to create squeezing\index{Squeezing!Atomic ensembles} and entanglement in atomic ensembles. The main methods exploit atom-light interactions in cold gases, or interactions between particles such as atom-atom collisions in Bose-Einstein condensates\index{Bose-Einstein condensates}, or combined electrostatic and ion-light interactions in ion chains. Atom-light interactions currently represent the most mature technology, and exhibit the highest squeezing of 20.1dB via an optical-cavity-based measurement \cite{bib:hosten2016measurement}.

@@

Many experimental methods have been developed for measuring and manipulating individual quantum systems, including single atoms in a cavity, trapped ions\index{Trapped ions}, and neutral atoms\index{Neutral atoms} in an optical lattice\index{Optical lattice}.

@@

There are two primary types of optical circuits: optical waveguides\index{Optical waveguides}, and fibre-loops\index{Fibre-loops}.

@@

The simplest approach to storing light is using an optical delay line\index{Delay line}, such as an optical fibre. Aside from loss, these also suffer that the storage time is fixed by the delay length, making on-demand output\index{On-demand output} extremely challenging without first having access to high-speed ($\sim$GHz) optical switches\index{Optical!Switches}.

>>>>

\subsection{Entangled states based on non-linear optics} \index{Non-linear!Optics}

@@

\subsection{Atomic ensembles} \index{Atomic!Ensembles}

A variety of techniques have been developed to create squeezing\index{Squeezing!Atomic ensembles} and entanglement in atomic ensembles. The main methods exploit atom-light interactions in cold gases, or interactions between particles such as atom-atom collisions in Bose-Einstein condensates\index{Bose-Einstein condensates (BECs)}, or combined electrostatic and ion-light interactions in ion chains. Atom-light interactions currently represent the most mature technology, and exhibit the highest squeezing of 20.1dB via an optical-cavity-based measurement \cite{bib:hosten2016measurement}.

@@

Many experimental methods have been developed for measuring and manipulating individual quantum systems, including single atoms in a cavity, trapped ions\index{Trapped ions}, and neutral atoms\index{Neutral atoms} in an optical lattice\index{Optical!Lattice}.

@@

There are two primary types of optical circuits: optical waveguides\index{Optical!Waveguides}, and fibre-loops\index{Fibre-loops}.

@@

The simplest approach to storing light is using an optical delay line\index{Delay line}, such as an optical fibre. Aside from loss, these also suffer that the storage time is fixed by the delay length, making on-demand output\index{On-demand!Output} extremely challenging without first having access to high-speed ($\sim$GHz) optical switches\index{Optical!Switches}.

### 2018-12-04 Sections/the_quantum_space_race.tex
indexing

The other important piece of technology is the acquisition, pointing, and tracking technology\index{Acquisition}\index{Pointing}\index{Tracking}, which allows the ground stations to track the location of the satellite as it moves across the sky (which is very rapid for LEO), and vice versa. This is achieved using lasers at separate wavelengths, and allows the photon transmission and the ground-based receivers to be pointing to each other to within $\sim 1.2$mrad \cite{bib:yin2017satellite}. The major aims of the project are to: perform QKD\index{Quantum key distribution (QKD)} between Xinglong and Urumqi (a ground distance of 2,500km); test Bell's inequality\index{Bell inequality} across a distance of 1,200km; and perform QST\index{Quantum state teleportation} between the satellite and Ali in Tibet (see Fig.~\ref{fig:space_4}). The final aim is to perform QKD between Beijing and Vienna (a distance of 7,500km that extends well beyond the Earth's curvature).

@@

For applications such as quantum clock synchronisation\index{Quantum clock synchronisation} (Sec.~\ref{sec:clock_sync}) and experiments testing fundamental physics at large length-scales and velocities, it is likely that extremely high fidelities of quantum operations will be required. For example, for clock synchronisation, even current atomic clocks\index{Atomic clocks} used as national standards have an accuracy at the level of 1 part in $10^{-14}$. Thus, such high-precision experiments will almost certainly follow the less demanding QKD experiments.

>>>>

The other important piece of technology is the acquisition, pointing, and tracking technology\index{Acquisition}\index{Pointing}\index{Tracking}, which allows the ground stations to track the location of the satellite as it moves across the sky (which is very rapid for LEO), and vice versa. This is achieved using lasers at separate wavelengths, and allows the photon transmission and the ground-based receivers to be pointing to each other to within $\sim 1.2$mrad \cite{bib:yin2017satellite}. The major aims of the project are to: perform QKD\index{Quantum key distribution (QKD)} between Xinglong and Urumqi (a ground distance of 2,500km); test Bell's inequality\index{Bell!Inequality} across a distance of 1,200km; and perform QST\index{Quantum state teleportation} between the satellite and Ali in Tibet (see Fig.~\ref{fig:space_4}). The final aim is to perform QKD between Beijing and Vienna (a distance of 7,500km that extends well beyond the Earth's curvature).

@@

For applications such as quantum clock synchronisation\index{Quantum clock synchronisation} (Sec.~\ref{sec:clock_sync}) and experiments testing fundamental physics at large length-scales and velocities, it is likely that extremely high fidelities of quantum operations will be required. For example, for clock synchronisation, even current atomic clocks\index{Atomic!Clocks} used as national standards have an accuracy at the level of 1 part in $10^{-14}$. Thus, such high-precision experiments will almost certainly follow the less demanding QKD experiments.
